### 2017-11-14 paper/sections/4_dynamic-policies.tex
paper: addresses #14 and #15
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% results: cache size trade-offs
\begin{figure}[t]
  \noindent\includegraphics[width=0.5\textwidth]{figures/methodology-tradeoff.png}\\
  \caption{The performance and resource utilization trade-off for different
  cache sizes. ``Baseline" is
  ParSplice unmodified and the ``Policy: Constrain Cache Size" graph limits the
  size of the cache to save memory.  \label{fig:methodology-tradeoff}}
\end{figure}

The results for different cache sizes for a growth rate of \(\Delta_1\) over a
2.5 hour run across 256 workers is shown in
Figure~\ref{fig:methodology-tradeoff}.  ``Baseline" is the performance of
unmodified ParSplice  measured in trajectory duration (\(y\) axis) and
utilization is measured with memory footprint of just the cache (\(y2\) axis).
The other graph shares the \(y\) axis and shows the trade-off of using a basic
LRU-style cache for different cache sizes, implemented using the ``when" and
``how much" policies in Figure~\ref{src:lru}.  The error bars are the standard
deviation of 3 runs.

\begin{figure}[t]
\footnotesize
\centering
\begin{minted}[xleftmargin=3em,linenos]{lua}
function when()
  if server[whoami]['cachesize'] > n then
    return true
  end
  return false
end

function howmuch()
  if servers[whoami]['cachesize'] > n
    return servers[whoami]['cachesize'] - n
  end
  return 0
end
\end{minted}
\caption{Policy that implements a basic LRU cache. The performance and memory
utilization for different values of \(n\) are graphed in
Figure~\ref{fig:methodology-tradeoff}.
\label{src:lru}}
\end{figure}

@@

% Why is this a good idea
Although ParSplice does not use a distributed file system, its workload is very
similar because the minima key-value store responds to small and frequent
requests, which results in hot spots and flash crowds.  Modern distributed file
systems have found efficient ways to measure, migrate, and partition metadata
load and have shown large performance gains and
better scalability~\cite{zheng:pdsw2014-batchfs, zheng:pdsw2015-deltafs,
grider:pdsw2015-marfs, ren:sc2014-indexfs, patil:fast2011-giga+,
brandt:msst2003-lh}.  Previous work quantified the speedups achieved with
Mantle and formalized balancers that were good for file systems.

@@

The actual policy is shown and described in more detail in the next section in
Figure~\ref{src:lru-dyn}, but the only difference between the code snippet in
Figure~\ref{src:lru} is the addition of lines 2-7.  We trigger the policy
switch at 100K keys to absorb the flash crowd at the beginning of the run. Once
triggered, keys are evicted to bring the size of the cache down to the
threshold.  In the bar chart, the cache sizes for the \(n\) key limit policy
are along the \(x\) axis.

>>>>

The results for different cache sizes for a growth rate of \(\Delta_1\) over a
2.5 hour run across 256 workers is shown in
Figure~\ref{fig:methodology-tradeoff}.  ``Baseline" is the performance of
unmodified ParSplice  measured in trajectory duration (\(y\) axis) and
utilization is measured with memory footprint of just the cache (\(y2\) axis).
The other graph shares the \(y\) axis and shows the trade-off of using a basic
LRU-style cache for different cache sizes, implemented using a ``when" policy
of \texttt{server[whoami]['cachesize']>n} and a ``how much" policy of
\texttt{servers[whoami]['cachesize']-n}. The error bars are the standard
deviation of 3 runs. 
%\begin{figure}[h] \footnotesize \begin{minted}{lua}
%server[whoami]['cachesize'] > n \end{minted} \end{figure}

%and ``how much":
%\begin{figure}[h]
%\footnotesize
%\begin{minted}{lua}
%servers[whoami]['cachesize'] - n
%\end{minted}
%\end{figure}

\begin{figure}[t]
\noindent\includegraphics[width=0.5\textwidth]{figures/methodology-tradeoff.png}\\
\caption{The performance and resource utilization trade-off for different cache
sizes. ``Baseline" is ParSplice unmodified and the ``Policy: Constrain Cache
Size" graph limits the size of the cache to save memory.
\label{fig:methodology-tradeoff}}
\end{figure}
%
%\footnotesize
%\centering
%\begin{minted}[xleftmargin=3em,linenos]{lua}
%function when()
%  if server[whoami]['cachesize'] > n then
%    return true
%  end
%  return false
%end
%
%function howmuch()
%  if servers[whoami]['cachesize'] > n
%    return servers[whoami]['cachesize'] - n
%  end
%  return 0
%end
%\end{minted}
%\caption{Policy that implements a basic LRU cache. The performance and memory
%utilization for different values of \(n\) are graphed in
%Figure~\ref{fig:methodology-tradeoff}.
%\label{src:lru}}
%\end{figure}

@@

%% Why is this a good idea
%Although ParSplice does not use a distributed file system, its workload is very
%similar because the minima key-value store responds to small and frequent
%requests, which results in hot spots and flash crowds.  Modern distributed file
%systems have found efficient ways to measure, migrate, and partition metadata
%load and have shown large performance gains and
%better scalability~\cite{zheng:pdsw2014-batchfs, zheng:pdsw2015-deltafs,
%grider:pdsw2015-marfs, ren:sc2014-indexfs, patil:fast2011-giga+,
%brandt:msst2003-lh}.  Previous work quantified the speedups achieved with
%Mantle and formalized balancers that were good for file systems.

@@

The actual policy is shown and described in more detail in the next section in
Figure~\ref{src:lru-dyn}.  We trigger the policy switch at 100K keys to absorb
the flash crowd at the beginning of the run. Once triggered, keys are evicted
to bring the size of the cache down to the threshold.  In the bar chart, the
cache sizes for the \(n\) key limit policy are along the \(x\) axis.
